File-based localization of numerical perturbations in data analysis pipelines

### 2020-03-29 paper.tex
Some fixes in methods

\toolname identifies the processes in a pipeline that produce different results when executed in two different conditions.  
In Condition 1, a directed, rooted, bipartite provenance graph is recorded for
each subject, where nodes represent application processes and files, and
edges represent read and write file accesses (Step 1 in Figure~\ref{fig:overview-tool}).
\emph{Transient} files are then identified as
 files that are either deleted during the execution, or modified by
multiple processes (Step 2). \toolname re-runs the pipeline to save these files
right after they are produced, resulting in a provenance \emph{DAG}
(Directed Acyclic Graph) in which file nodes have a single parent (in-degree
of 1) (Step 3) \tristan{Ali, this is not true in Figure 1: at step 3 there are still transient files}. This DAG is then compared to the one produced from
Condition 2, in a step-by-step execution to prevent the propagation of differences (step 4).
\toolname finally produces a labeled graph that identifies the
non-reproducible processes of the pipeline.

\toolname makes the following assumptions on the pipeline, meant to ensure that 
a file can be unambiguously associated with the process that created it:
\begin{enumerate}
  \item Files are not written concurrently by different processes, although sequential writes by multiple processes are supported;
  \item In case a process writes multiple versions of the same file, only a single version is made available to other processes.
  \item Temporary files are not removed by the processes that create them.
\end{enumerate} 
In addition, \toolname also requires that processes are associated to a
command line (executable and arguments), to facilitate process instrumentation.

@@

@@

Provenance graphs may be subject-dependent, which justifies the processing
of multiple subjects. For instance, data acquisitions may be
repeated a different number of times in each subject, for noise-reduction
purposes. Some of these differences can be neglected, for instance when a
data decompression step is present at the beginning of the execution for
some subjects only, but other differences cannot, for instance
when complete different processing paths are used in different subjects.

@@

\toolname captures temporary files in Condition 1 by replacing every
process P by a wrapper that first calls P and then saves the produced
temporary files to a read-only directory. This process replacement does not require 
modifying the pipeline: it only pre-pends to the \texttt{PATH} environment
variable a directory containing a wrapper script named after the executable
called by P.

@@

As an example, in the sample pipeline in
Listing~\ref{listing:sample-script}, file \emph{output.nii.gz} is first written
by \texttt{73\#bet2} and then overwritten by process \texttt{75\#fslmaths} as a temporary file.

>>>>

\toolname identifies the processes in a pipeline that produce different results when executed in two different conditions.  
In Condition 1, a directed, rooted, bipartite provenance graph is recorded for
each subject, where nodes represent application processes and files, and
edges represent read and write file accesses (Step 1 in Figure~\ref{fig:overview-tool}).
\emph{Transient} files are then identified as
 files that are either deleted during the execution, or modified by
multiple processes (Step 2). \toolname re-runs the pipeline to save these files
right after they are produced, resulting in a provenance \emph{DAG}
(Directed Acyclic Graph) in which file nodes have a single parent (in-degree
of 1) (Step 3) \tristan{Ali, this is not true in Figure 1: at step 3 there are still transient files}. This DAG is then compared to the one produced from
Condition 2, in a step-by-step execution that prevents the propagation of differences (Step 4).
\toolname finally produces a labeled graph that identifies the
non-reproducible processes of the pipeline.

\toolname makes the following assumptions on the pipeline, meant to ensure that 
a file can be unambiguously associated with the process that created it:
\begin{enumerate}
  \item Files are not written concurrently by different processes, although sequential writes by multiple processes are supported.
  \item In case a process writes multiple versions of the same file, only a single version is made available to other processes.
  \item Temporary files used by multiple processes are not removed by the process that created them. \tristan{explain}
\end{enumerate} 
In addition, \toolname also requires that processes are associated to a
command line (executable and arguments), to facilitate process instrumentation.

@@

\tristan{The text switches between active and passive voice, this should be fixed.}

@@

Provenance graphs are often subject-dependent.
%, which justifies the processing
% of multiple subjects. For instance, data acquisitions may be
% repeated a different number of times in each subject, for noise-reduction
% purposes. 
Some of these differences can be neglected, for instance when a
data decompression step is present at the beginning of the execution for
some subjects only, but other differences cannot, for instance
when complete different processing paths are used in different subjects.

@@

\toolname captures temporary files by replacing every
process P by a wrapper that first calls P and then saves the produced
temporary files to a read-only directory. This process replacement does not require 
modifying the pipeline: it only pre-pends to the \texttt{PATH} environment
variable a directory containing a wrapper script named after the executable
called by P.

@@

As an example, in the sample pipeline in
Listing~\ref{listing:sample-script}, file \emph{output.nii.gz} is first written
by \texttt{73\#bet2} and then overwritten by process \texttt{75\#fslmaths} as a temporary file. 
\tristan{add this comment to caption}
